---
name: Matthew J Grainger
position: "Researcher"
address: "Norwegian Institute for Nature Research"
phone: 
www: uncertainecologist.netlify.com
email: "Matthew.Grainger@nina.no"
twitter: Ed_pheasant
github: DrMattG
aboutme: Wildlife, Uncertainty, Evidence synthesis, Decision models
date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::awesomecv:
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(RefManageR)
library(vitae)
library(scholar)
source("C:/Users/matthew.grainger/Documents/Employment_Docs/Markdown_CV/Robjhyndman_Baretable.R")
```

# About me

I am an ecologist, with research interests in how we use knowledge to better inform decision making in species conservation (i.e. "Evidence-based decision making"). I develop opensource tools (in R and Shiny) that help people gather information robustly in a transparent way, interact with that information and make inference from it.

I am currently working on several projects that are fundamentally about how we make open research approaches (i.e. sharing data, sharing code, sharing best practice) as an integrated part of the workflow for biodiversity researchers and how we can take this open research and use it to help decision-makers find optimal solutions.


# Education and qualifications

```{r degrees, results='asis'}
tribble(

  ~ degree, ~ uni, ~ loc, ~ dates,

  "BSc (Hons) in Zoology", "Newcastle University", "UK", "1994 - 1997",

  "MSc in Conservation & planning", "University of Pretoria", "South Africa", "2004 - 2005", 

  "PhD Zoology", "University of Pretoria", "South Africa", "2008 - 2012" 
) %>% 

  detailed_entries(degree, dates, uni, loc)

```

# Employment history


```{r employment, results='asis'}

tribble(
  
  ~Start, ~End, ~Position,
  
  2005, 2006, "\\textbf{ Research Co-ordinator}, Frontier-Tanzania, Tanzania",
  
  2011, 2012, "\\textbf{ Conservation Research and Support Officer}, World Pheasant Ass., Newcastle, UK",
  
  2013, 2014, "\\textbf{ Postdoctoral Research Associate-Research Impact}, Newcastle University, UK",
  
  2014, 2019, "\\textbf{ Postdoctoral Research Associate}, Newcastle University, UK",
  
  2019, 2021, "\\textbf{ Postdoctoral Fellow}, NINA, Trondheim, Norway",
  2021, NA , "\\textbf{ Researcher}, NINA, Trondheim, Norway"
  
) %>%
  
  arrange(-Start) %>%
  
  #filter(Start > 2000) %>%
  
  mutate(End = replace_na(End, "")) %>%
  
  mutate(Years = paste(Start, "--", End, sep = "")) %>%
  
  select(Years, Position) %>%
  
  baretable()

```

# R packages

```{r}
library(dplyr)
#knitr::write_bib(c("citationchaser", "sysrevdata"), "MattRpacks.bib")

bibliography_entries("MattRpacks.bib") %>%
  arrange(desc(author$family), issued)
```

# R packages in development

```{r}
library(dplyr)
#knitr::write_bib(c("citationchaser", "sysrevdata"), "MattRpacks.bib")

bibliography_entries("MattRpacks.bib") %>%
  arrange(desc(author$family), issued)
```


# Publications

```{r}
scholar::get_publications("aZ4E5I4AAAAJ&hl") %>%

  arrange(desc(year)) %>%

  detailed_entries(

    what = title,

    when = year,

    with = author,

    where = journal

  )
```
